Galois Slicing as Differentiation

### 2025-07-11 main/introduction.tex
Delete.

Previous work on \GPS used a special operational semantics to generate a trace of each execution, and then separately used that trace to compute the Galois connection described above, by re-running forwards or backwards over the trace. It would be useful to have a denotational account of \GPS as well, especially if we could provide a semantics where the backwards analysis is baked in, rather than provided by a separately (but somewhat redundantly) defined ``backwards evaluation'' operation. As it happens there is a close analogy between \GPS and \emph{automatic differentiation} for differentiable programs~\cite{siskind08,elliott18,vakar22}, which points to a way to develop such an approach. We have already hinted at this in the description above, but let us now make it explicit.

>>>>

Previous work on \GPS used a special operational semantics to generate a trace of each execution, and then separately used that trace to compute the Galois connection described above, by re-running forwards or backwards over the trace. It would be useful to have a denotational account of \GPS as well, especially if we could provide a semantics where the backwards analysis is baked in, rather than provided by a separately defined ``backwards evaluation'' operation. As it happens there is a close analogy between \GPS and \emph{automatic differentiation} for differentiable programs~\cite{siskind08,elliott18,vakar22}, which points to a way to develop such an approach. We have already hinted at this in the description above, but let us now make it explicit.
